Thesis Draft

### 2015-10-26 chapter2.tex
reorganization
Former-commit-id: c8f73de447b8554d6ab2083ae746442981971ac8

\chapter{Theory of Trash}

@@

WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles to giant dozers that moves and piles trash in the landfills.

@@

>>>>

\chapter{Trash in Theory}

@@

(WALL-E is a 2008 American computer-animated science-fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles to giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that has no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks.)

@@

Thompson and Zubiaurre say trash moves between value states, Zizek says you must love your trash and bricolage can be the name of this practice.

### 2015-10-26 chapter3.tex
reorganization
Former-commit-id: c8f73de447b8554d6ab2083ae746442981971ac8

% TODO praphase
\textbf{[TODO praphrase]} "The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic_drum2.png}
        \caption{Drum}
        \label{fig:mouse}
    \end{subfigure}
    \caption{Pictures of instruments}\label{fig:animals}
\end{figure}

>>>>

% TODO praphase
[TODO praphrase] \quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996}  \cite{tauxe2012encyclopedia}.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic_drum2.png}
        \caption{Drum}
        \label{fig:mouse}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}
